MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-06-23 MAESTROeX_I/paper.tex

\correspondingauthor{Doreen Fan; DFan@lbl.gov}

\author[0000-0002-3246-4315]{Duoming Fan}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author[0000-0003-1791-0265]{Andrew Nonaka}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author[0000-0003-2103-312X]{Ann S. Almgren}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

>>>>

\correspondingauthor{Duoming Fan; DFan@lbl.gov}

\author[0000-0002-3246-4315]{Duoming Fan}
\affil{Lawrence Berkeley National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author[0000-0003-1791-0265]{Andrew Nonaka}
\affil{Lawrence Berkeley National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author[0000-0003-2103-312X]{Ann S. Almgren}
\affil{Lawrence Berkeley National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}
